---
title: "AutoIV example neat"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

Using "AutoIV example neat" as template to acquire TEVC I V data from .abf files, you will only need to change parameters in stage 1. There is no need to change anything in stage 2-4.

AutoIV is the streamlined I V data acquisition procedure that uses the GitHub packages imlijunda/abf2load and Crystal-YWu/vcfunc.

If you haven't installed abf2load and vcfunc, please refer to "vcfunc example.Rmd" for how to install. Also, "AutoIV example.Rmd" contains more detailed description of how to use AutoIV.
https://github.com/Crystal-YWu/vcfunc/tree/master/vcfunc%20example


# Case study experiment set up
Please refer to "vcfunc example.Rmd" for experiment set up details.

# AutoIV stage 1: user defined parameters
Define parameters according to your experiment set up and click run:
```{r warning=FALSE}
library(tidyverse)
library(abf2load)
library(vcfunc)

index=read_csv('sample data file index.csv')
folder='sample data'

# Oocyte 1 to 20 were tested with NO3 (N) buffers, while oocyte 21 to 37 were tested with Cl (C) buffers.
C = c(21:37)
N = c(1:20)

# For gene "A2" and NO3 buffer tested oocytes "N"
Gene = "A2"
OocyteNo = N

# Define list names (user defined names):
    # 1. a list for buffer names
    ListBufferNames = "proc_nameA2N"  
    # 2. a list containing summary (mean and SEM) of all selected oocytes
    ListMeanSEM = "proc_meanVAA2N"
    # 3. a list for voltage and current of each oocyte
    ListIV = "proc_VAA2Ni"
    # 4. a list for currents of each oocyte
    ListI = "proc_VAA2Nicurrent"

# Create a list of buffer name as on the data file index
BufferNameIdx = c("B","1N","5N","10N","25N","50N","100N")
# Create a list of full buffer names corresponding to the index buffer names
  BufferNameFull = c("Basal","1mM NO3","5mM NO3","10mM NO3","25mM NO3","50mM NO3","100mM NO3")

# Turn on automatic backward interval search method? TRUE or FALSE
  # When FALSE, search interval using the default method: automatic most stable interval method
backward_interval_search = FALSE  
  
# Enable plot? TRUE or FALSE
  # Note that when plot wave form is enabled, the speed of running stage 2 will be very very slow
enable_plot = FALSE
```

# AutoIV stage 2: I V acquisition loop
This stage is a loop which will acquire all your I V data from your .abf files in one run.

Stage 2 could be slow depending on your total file size and whether plot is enabled.

Click run:
```{r}
# Create lists using the list names defined in stage 1
    eval(parse(text=paste(ListBufferNames, " = list()",sep="")))
    eval(parse(text=paste(ListMeanSEM, " = list()",sep="")))
    eval(parse(text=paste(ListIV, " = list()",sep="")))
    eval(parse(text=paste(ListI, " = list()",sep="")))

for (idx in 1:length(BufferNameIdx)){
  # Select file names from index
  selected = select_samples(dataindex = index, 
                            oocyteNo = OocyteNo, 
                            gene = Gene, 
                            buffer = BufferNameIdx[[idx]])
  nselected = nrow(selected)
  
  # Load data into R
  abf_raw = abf2.load_in_folder(folder = "sample data/",
                                  filename_list = unlist(selected[, "FileName"]))
  abf_list = abf_raw
  abf_title = unlist(selected[, "FileName"])
  
  # Define “cursor” position using automatic method
  intv_list = FindAllSamplingInterval(abf_list, backward_seach = backward_interval_search)
  # Plot the waveforms, and the interval is between the 2 dash lines.
  if (enable_plot){
    p = PlotAll_IVChannelWithIntv(abf_list, intv_list, title_list = abf_title)
    print(p)
  }
  
  # I V data extraction
    # Calculate the mean V and I values inside the intervals
  df_mean_voltage = AllSamples_VoltageMeans(abf_list, intv_list)
  df_mean_current = AllSamples_CurrentMeans(abf_list, intv_list)
  
  # Calculate the average V and I values (and SEM) for all selected oocytes:
  df_summary = AllSamples_IVSummary(abf_list, intv_list)
  # Extract V and I values (or I only) for each oocyte:
  individuals = AllSamples_IVRaw(abf_list, intv_list)
  individualsI = AllSamples_IRaw(abf_list, intv_list)
  
  # Save the extracted data into the the 4 predefined lists:
  eval(parse(text=paste(ListBufferNames, "[[idx]]"," = BufferNameFull[idx]",sep="")))
  eval(parse(text=paste(ListMeanSEM, "[[idx]]"," = df_summary",sep="")))
  eval(parse(text=paste(ListIV, "[[idx]]"," = individuals",sep="")))
  eval(parse(text=paste(ListI, "[[idx]]"," = individualsI",sep="")))
}
```

# AutoIV stage 3: export data to .csv files
Data in .csv files can be copy and paste into other programs for graphing.
```{r}
# Export the list containing currents of each oocyte to .csv files
wd = getwd()
for (i in 1:length(BufferNameIdx)){
  filename = paste(wd, "/I data ", 
                  Gene, 
                  " ", 
                  BufferNameFull[[i]], 
                  ".csv", 
                  sep="")
  write.csv(eval(parse(text=paste(ListI, "[[i]]",sep=""))),filename)
}
```
You can also export the other 3 data lists to .csv files.

# AutoIV stage 4: quick I V plot in R
```{r echo=TRUE}
# Use the list containing summary data, set name of each element to buffer names
eval(parse(text=paste("names(", ListMeanSEM, ")"," = BufferNameFull",sep="")))
# Plot
PlotAll_IVSummary(get(ListMeanSEM))
```

