---
title: "AutoIV example"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

AutoIV is the streamlined I V data acquisition procedure that uses the GitHub packages imlijunda/abf2load and Crystal-YWu/vcfunc.


AutoIV uses the automatic most stable interval method to acquire I and V data from wave form plots. Users can change the method to either Automatic backward search method or Manual define interval method. Examples of all 3 methods can be found in "vcfunc example.Rmd" in:

https://github.com/Crystal-YWu/vcfunc/tree/master/vcfunc%20example

When intervals cannot be found by an automatic interval selection method, result will return NA and this will be reflected in the final output data. 

If you haven't installed abf2load and vcfunc, please refer to "vcfunc example.Rmd" for how to install.

# Case study experiment set up
Xenopus laevis oocytes were injected with either cRNA of gene "A2" or water 2 days before experiment.

A two electrode voltage clamp rig is used for voltage clamp of the oocytes.

Voltage step protocol: 11 steps, from -120mV to +80mV, +20mV per step

- Time settings: 300 ms hold – 550 ms voltage steps – 350 ms hold
- Total time per sweep: 1.2s

Two sets of experiments were performed:

- Run voltage step protocol on oocytes using Basal buffer and 1-100 mM Cl buffers
- Run voltage step protocol on oocytes using Basal buffer and 1-100 mM NO3 buffers: 1N, 5N, 10N, 25N, 50N, 100N

# Data file index
A file index is required for identifing the .abf data files. 

Important information about the format of file index:

- 1. Please DO NOT change or remove any column names except for "RestingVoltage" and "Comments".
- 2. When a data file contains Gap free type data, put "Gapfree" in the corresbonding row under the "DataType" column, then the select_samples() function will auto filter out the Gap free data.
- 3. When a data file is NOT to be included in the analysis, put "yes" in the corresbonding row under the "DIsregard?" column, then the select_samples() function will auto filter out the disregarded data.
- 4. Any of the column except for "FileName" can be left empty, when the experiment is not as complicated as the experiment in this case study.

# AutoIV stage 1: user defined parameters
```{r warning=FALSE}
# Load packages
library(tidyverse)
library(abf2load)
library(vcfunc)

# Load data file index and define .abf data file folder path
index=read_csv('sample data file index.csv')
folder='sample data'

# Define factors for data sorting
  # Oocyte 1 to 20 were tested with NO3 (N) buffers, while oocyte 21 to 37 were tested with Cl (C) buffers.
C = c(21:37)
N = c(1:20)

# Define Gene and buffer (N or C) to be analysed
  # For A2 N buffers:
Gene = "A2"
OocyteNo = N

# create empty lists to put data in 
  ### When your own user defined list names, remember to also change the list names in stage 2 and stage 3
    # 1. a list for buffer names
    proc_meanVAA2N = list()
    # 2. a list containing summary (mean and SEM) of all selected oocytes
    proc_nameA2N = list()
    # 3. a list for voltage and current of each oocyte
    proc_VAA2Ni = list()
    # 4. a list for currents of each oocyte
    proc_VAA2Nicurrent = list()

# Create a list of buffer name as on the data file index
  # This vector is used in stage 2
BufferN = c("B","1N","5N","10N","25N","50N","100N")
# (Optional) Create a list of full buffer names corresponding to the index buffer names
  # This vector is used in stage 3 and 4. If full names are not defined, remember to change "BuffersN" to "BufferN" in stage 3 and 4
  BuffersN = c("Basal","1mM NO3","5mM NO3","10mM NO3","25mM NO3","50mM NO3","100mM NO3")
  
# Enable plot? TRUE or FALSE
  # Note that when plot wave form is enabled, the speed of running stage 2 will be very very slow
enable_plot = FALSE
```

# AutoIV stage 2: I V acquisition loop
This stage is a loop which will acquire all your I V data from your .abf files in one run.

Stage 2 could be slow depending on your total file size and whether plot is enabled.

You can change the script in "Define cursor position using automatic most stable interval method" section to other interval definition methods.
```{r}
for (idx in 1:length(BufferN)){
  # Select file names from index
  selected = select_samples(dataindex = index, 
                            oocyteNo = OocyteNo, 
                            gene = Gene, 
                            buffer = BufferN[[idx]])
  # Count the number of data files selected
  nselected = nrow(selected)
  
  # Load data into R
  abf_raw = abf2.load_in_folder(folder = "sample data/",
                                  filename_list = unlist(selected[, "FileName"]))
  abf_list = abf_raw
  abf_title = unlist(selected[, "FileName"])
  
  ### Define “cursor” position using automatic most stable interval method
  intv_list = FindAllSamplingInterval(abf_list)
  # Plot the waveforms, and the interval is between the 2 dash lines.
  if (enable_plot){
    p = PlotAll_IVChannelWithIntv(abf_list, intv_list, title_list = abf_title)
    print(p)
  }
  
  # I V data extraction
    # Calculate the mean V and I values inside the intervals
  df_mean_voltage = AllSamples_VoltageMeans(abf_list, intv_list)
  df_mean_current = AllSamples_CurrentMeans(abf_list, intv_list)
  
  # Calculate the average V and I values (and SEM) for all selected oocytes:
  df_summary = AllSamples_IVSummary(abf_list, intv_list)
  # Extract V and I values (or I only) for each oocyte:
  individuals = AllSamples_IVRaw(abf_list, intv_list)
  individualsI = AllSamples_IRaw(abf_list, intv_list)
  
  ### Save the extracted data into the the 4 predefined lists:
  proc_VAA2Ni[[idx]] = individuals
  proc_VAA2Nicurrent[[idx]] = individualsI
  proc_meanVAA2N[[idx]] = df_summary
  proc_nameA2N[[idx]] = BuffersN[idx]
}
```

# AutoIV stage 3: export data to .csv files
Only one processed data list is exported to .csv files in this example.

- Data in .csv files can be copy and paste into other programs for graphing.
```{r}
### Export the list containing currents of each oocyte to .csv files
wd = getwd()
for (i in 1:length(proc_nameA2N)){
  filename = paste(wd, "/I data ", 
                  Gene, 
                  " ", 
                  BuffersN[[i]], 
                  ".csv", 
                  sep="")
  write.csv(proc_VAA2Nicurrent[[i]],filename)
}
```
You can also export the other 3 data proc_ data lists to .csv files.

# AutoIV stage 4: quick I V plot in R
```{r echo=TRUE}
# Use the list containing summary data, set name of each element to buffer names
names(proc_meanVAA2N) = BuffersN
# Plot
PlotAll_IVSummary(proc_meanVAA2N)
```

